Variational Monte Carlo on bosonic systems

### 2018-03-23 project_1/article/article.tex
Wrote gradient descent theory

		The method of

@@

    We will start without importance sampling, that is by employing the simpler and more naïve "brute force" Monte Carlo
    sampling. Moreover, we will compute the value for the local energy analytically as well as with a numerical approach.
    In the numerical approach we employ the well-know approximation for the second derivative,
    \begin{equation}
    		f''(x= \approx \frac{f(x-h) - 2f(x) + f(x+h)}{h^2}.
    \end{equation}

>>>>

		Scanning the entire space of variational parameters can be a somewhat despairing task. To aid us in the search we
		therefore implement the method of gradient descent\footnote{Also known as steepest descent, easily confused
		with the steepest descent method for integation.}. In any optimum we generally have that the derivative should equal
		zero. In our case, we want to find the minimum of the expected local energy with respect to some variational
		parameter $\alpha$, so that
		\begin{equation}
			\nabla_\alpha \expval{E_L(\mathbf{R}; \alpha)} = 0.
		\end{equation}	
		The foundation for  the method of gradient descent lies in the fact that some analytic
		\footnote{We use the term analytic quite recklessly.} function $F(\alpha)$ decreases fastest in the direction
		of $-\nabla_\alpha F(\alpha)$. This means that we could eventually get to an ensuing minimum by trailing along the
		pathway of the following recursive relation,
		\begin{equation}
			\alpha_{k+1} = \alpha_k - \gamma \nabla_{alpha k} F(\alpha_k).
		\end{equation}
		If $\gamma$ is small enough we should have $f(\alpha_k) \geq F(\alpha_{k+1})$ for all $k$ and hopefully we will
		experience convergence to the desired minimum.

		For our special case : INSERT DERIVATION OF LOCAL ENERGY??

@@

    We will start without importance sampling, that is by employing the simpler and more naïve "brute force" Monte Carlo
    sampling. Moreover, we will compute the value for the local energy analytically as well as with a numerical approach.
    In the numerical approach we employ the well-know approximation for the second derivative,
    \begin{equation}
    		f''(x)= \approx \frac{f(x-h) - 2f(x) + f(x+h)}{h^2}.
    \end{equation}
